---
title: "Activity 6 - Logistic Regression"
output: github_document
editor_options: 
  markdown: 
    wrap: 80
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Necessary Packages

```{r import, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
```

## Load Data and

```{r load-data, message=FALSE, warning=FALSE}
resume <- readr::read_csv("https://www.openintro.org/data/csv/resume.csv")

head(resume)
```


-   Is this an observational study or an experiment? Explain. Ans

-   The variable of interest is `received_callback`. What type of variable is
    this? What do the values represent?
    
    Boolean variable

```{r}
unique(resume$received_callback)
```

-   For `received_callback`, create an appropriate data visualization using
    `{ggplot2}`. Be sure to provide more descriptive labels (both axes labels
    and value labels - there are many ways to do this) as well as an appropriate
    title.
    
```{r}
resume %>%
  ggplot(aes(x=received_callback))+
  geom_bar()+
  theme_minimal()
```


-   Below, I provide you with a numerical summary table that should reiterate
    (i.e., provides numerical values) your plot in (3). Write the code to
    produce this table.

    | received_callback |    n | percent |
    |:------------------|-----:|--------:|
    | No                | 4478 |   91.95 |
    | Yes               |  392 |    8.05 |
    
```{r}
resume %>%
  str_replace(received_callback, "0", "No") %>%
  select(received_callback) %>%
  group_by(received_callback) %>%
  summarise(n=n()) %>%
  mutate(persent = round((n/sum(n)) * 100, 2))

```


-   Using the output from (4) and (5), what do you notice?
